Chord: A Versatile Platform for Program Analysis

### 2011-04-15 main/doc/arch.tex
more documentation

\xname{architecture}
\chapter{Architecture of Chord}
\label{chap:architecture}

@@

\begin{center}
\includeimage{0.7}{chord_arch.png}
%\texonly{\includegraphics[scale=0.7]{chord_arch.png}}
%\htmlonly{{\htmlimg{chord_arch.png}}}
\end{center}

@@

The Java program to be analyzed is also specified via properties.
%These properties are described in Section \ref{sec:program-props}.
Chapter \ref{chap:program-setup} describes how to setup a Java program for analysis using Chord.
Chord analyzes Java bytecode, not Java source code, and thus only requires
the program's class files.  Certain analyses, however, present
their results at the Java source code level, and thus require the program's
Java source files as well.

\subsubsection*{Program Representation}

Chord uses the \xlink{Joeq}{http://joeq.sourceforce.net/} Java compiler framework
to convert the Java bytecode of the input Java program, one class file at a time,
into a three-address-like intermediate program representation called {\it quadcode}
that is more suitable for analysis. Chapter \ref{chap:program-representation}
describes the quadcode representation in detail.

@@

A pre-requisite to analyzing a Java program using any program analysis framework, including Chord, is
to compute the {\it analysis scope}: which parts of the program to analyze.  Chord implements
several standard scope construction algorithms from the literature that differ in aspects such as
scalability, precision, and usability for the problem at hand.  Chapter \ref{chap:computing-scope}
describes these algorithms in detail.

@@

@@

Chord can be invoked in one of two modes: classic or modern.
These two modes defer in the semantics of dependencies between analyses.  In particular, the classic mode
is simpler to understand for novice users (the dependencies are only data dependencies) but has a sequential
runtime, whereas the modern mode is harder to understand (there are both data and control dependencies)
but has a parallel runtime that is capable of running analyses without dependencies between
them in parallel.  The parallel runtime is based on \xlink{Habanero-Java}{http://habanero.rice.edu/hj.html},
and the semantics of the dependencies between analyses is based on the
\xlink{Habanero Concurrent Collections (CnC)}{http://habanero.rice.edu/cnc.html} declarative parallel
programming model.

Chapter \ref{chap:project} describes how to write and run analyses in Chord.

\subsubsection*{Analysis Templates}

Chord provides various {\it analysis templates}: classes containing boilerplate code that can be
extended by users to rapidly prototype different kinds of analyses.  An example is class RHSAnalysis,
named after [Reps, Horowitz, and Sagiv 1995], which can be extended by users to write a summary-based inter-procedural
context-sensitive static analysis by merely specifying the abstract domain and intra-procedural transfer functions.
Another example is DynamicAnalysis, which can be extended by
users to write a dynamic analysis by merely specifying which of various provided events to instrument, and
the transfer functions for those events.
Chapter \ref{chap:analysis-templates} describes the various analysis templates.

@@

Chord uses the \xlink{Javassist}{http://www.javassist.org/} Java bytecode manipulation
framework for instrumenting bytecode and doing dynamic analysis.
Chord offers the most versatile capabilities of any existing dynamic analysis framework
for Java, particularly the ability to instrument the entire JDK (including classes in
package java.lang).
Specifically, it includes support for:
\begin{itemize}
\item
offline as well as load-time instrumentation of Java bytecode;
\item
processing of dynamic analysis events online in the same JVM or offline in a different JVM with an uninstrumented JDK (the latter circumvents performance and correctness problems that can arise if a single JVM with an instrumented JDK is used to generate and handle events); and
\item
allowing the event-generating and event-handling JVMs to run either serially (by storing the entire trace of events to a regular file) or in parallel (by streaming the trace of events in a piped file).
\end{itemize}
Chapter \ref{chap:dynamic-analysis} describes all aspects of dynamic analysis in Chord.

@@

An analysis in Chord can be written either imperatively in Java or declaratively in Datalog.
Chord uses the BDD-based Datalog solver \xlink{bddbddb}{http://bddbddb.sourceforge.net/} to
run analyes written in Datalog.
Chapter \ref{chap:datalog-analysis} describes all aspects of Datalog analysis.

%If the analyses are purely static, it suffices to specify the main class of the program
%(via property \code{chord.main.class}) and the application classpath of the program (via property \code{chord.class.path}).
%If the analyses need to present their results at the Java source level, then
%the path of the program's Java source files is also required (via property \code{chord.src.path}).
%Finally, if any analysis is dynamic, then the command-line arguments to be used for running the
%program must also be specified (via property \code{chord.run.ids} and properties \code{chord.args.<N>} for
%each item \code{<N>} in the value of property \code{chord.run.ids}).

\subsubsection*{Predefined Analyses}

Chapter \ref{chap:predefined-analyses} describes many standard analyses that are implemented in Chord.

>>>>

\xname{arch}
\chapter{Architecture of Chord}
\label{chap:arch}

@@

\begin{center}
\includeimage{0.7}{chord_arch.png}
\end{center}

@@

The Java program to be analyzed is also specified via properties.  Chapter
\ref{chap:setup} describes how to setup a Java program for analysis using Chord.
Chord analyzes Java bytecode, not Java source code, and thus only requires the
program's class files.  Certain analyses, however, present their results at the
Java source code level, and thus require the program's Java source files as
well.

\subsubsection*{Java Program Representation}

Chord uses the \xlink{Joeq}{http://joeq.sourceforce.net/} Java compiler
framework to convert the Java bytecode of the input Java program, one class file
at a time, into a three-address-like intermediate program representation called
{\it quadcode} that is more suitable for analysis. Chapter
\ref{chap:program} describes the quadcode representation in detail.

@@

A pre-requisite to analyzing a Java program using any program analysis
framework, including Chord, is to compute the {\it analysis scope}: which parts
of the program to analyze.  Chord implements several standard scope construction
algorithms from the literature that differ in aspects such as scalability,
precision, and usability for the problem at hand.  Chapter \ref{chap:scope}
describes these algorithms in detail.

@@

Chord provides many standard analyses.  Chapter \ref{chap:predefined} describes
these analyses and how to run them.  Moreover, Chord allows users to define
their own analyses, possibly atop the provided analyses.

@@

Chord can be invoked in one of two modes: {\it classic} or {\it modern}.  These
two modes defer in the semantics of dependencies between analyses.  In
particular, the classic mode is simpler to understand for novice users (the
dependencies are only data dependencies) but has a sequential runtime, whereas
the modern mode is harder to understand (there are both data and control
dependencies) but has a parallel runtime that is capable of running analyses
without dependencies between them in parallel.  The parallel runtime is based on
\xlink{Habanero-Java}{http://habanero.rice.edu/hj.html}, and the semantics of
the dependencies between analyses is based on the
\xlink{Habanero Concurrent Collections (CnC)}{http://habanero.rice.edu/cnc.html}
declarative parallel programming model.

Chapter \ref{chap:project} expands upon the modular architecture of analyses in
Chord that is described above.

Chord provides various {\it analysis templates}: classes containing boilerplate
code that can be extended by users to rapidly prototype different kinds of
analyses.  An example is class RHSAnalysis, named after [Reps, Horowitz, and
Sagiv 1995], which can be extended by users to write a summary-based
inter-procedural context-sensitive static analysis by merely specifying the
abstract domain and intra-procedural transfer functions.  Another example is
DynamicAnalysis, which can be extended by users to write a dynamic analysis by
merely specifying which of various provided events to instrument, and the
transfer functions for those events.

Chapters \ref{chap:writing} and \ref{chap:running} describe how to write and run
your own analyses in Chord using the provided analysis templates.

@@

Chord uses the \xlink{Javassist}{http://www.javassist.org/} Java bytecode
manipulation framework for instrumenting bytecode and doing dynamic analysis.
Chord offers the most versatile capabilities of any existing dynamic analysis
framework for Java, particularly the ability to instrument the entire JDK
(including classes in package java.lang).  Specifically, it includes support
for:

\begin{itemize}
\item
offline as well as load-time instrumentation of Java bytecode;
\item
processing of dynamic analysis events online in the same JVM or offline in a
different JVM with an uninstrumented JDK (the latter circumvents performance and
correctness problems that can arise if a single JVM with an instrumented JDK is
used to generate and handle events); and
\item
allowing the event-generating and event-handling JVMs to run either serially
(by storing the entire trace of events to a regular file) or in parallel (by
streaming the trace of events in a piped file).
\end{itemize}

Chapter \ref{chap:dynamic} describes all aspects of dynamic analysis in Chord.

@@

A common way to rapidly prototype an analysis in Chord is using a declarative
logic-programming language called Datalog.  Chord uses the BDD-based Datalog
solver \xlink{bddbddb}{http://bddbddb.sourceforge.net/} to run analyes written
in Datalog.  Chapter \ref{chap:datalog} describes all aspects of such analyses.

### 2011-04-15 main/doc/datalog.tex
more documentation

\xname{datalog_analysis}
\chapter{Datalog Analysis}
\label{chap:datalog-analysis}

A common way to rapidly prototype analyses in Chord is using a declarative
logic-programming language called Datalog.  This chapter describes all aspects of
Datalog analyses in Chord.
Section \ref{sec:writing-datalog-analysis} explains how to write and run a Datalog analysis.
Section \ref{sec:tuning-datalog-analysis} explains how to tune its performance.
Finally, Section \ref{sec:bdd} explains the representation of BDDs (Binary Decision Diagrams)
which are a data structure central to executing Datalog analyses.

\section{Writing a Datalog Analysis}
\label{sec:writing-datalog-analysis}

A Datalog analysis declares a bunch of input/output program relations,
each over one or more program domains, and provides a bunch of rules (constraints)
specifying how to compute the output relations from the input relations.
It can be defined in any file with extension {\tt .dlog}
in any directory in the path specified by property \code{chord.dlog.analysis.path}.
An example Datalog analysis is shown below:

@@

The ``\code{.include "<DOM_NAME>.dom"}'' lines specify each program domain named
\code{<DOM_NAME>} that is needed by the Datalog analysis, i.e., each domain over which
any program relation that is input/output by the Datalog analysis is defined. 
The declaration of each such relation specifies the domain of each of the relation's attributes.
If the same domain appears in multiple attributes of a relation then
contiguous integers starting from 0 must be used to distinguish them; for instance,
in the above example, {\tt candidate} is a binary relation, both of whose
attributes have domain {\tt E}, and they are distinguished as {\tt E0} and {\tt E1}.

@@

Each Datalog analysis rule is a Horn clause of the form
``{\tt R(t) :- R1(t1), ..., Rn(tn)}"
meaning that if relations {\tt R1}, ..., {\tt Rn} contain tuples {\tt t1}, ..., {\tt tn}
respectively, then relation {\tt R} contains tuple {\tt t}.
A backslash may be used at the end of a line to break long rules for readability.
The Datalog analysis solver bddbddb used in Chord does not apply any
sophisticated optimizations to simplify the rules; besides the BDD variable order,
the manner in which these rules are expressed heavily affects the performance of
the solver.  For instance, an important manual optimization involves breaking down
long rules into multiple shorter rules communicating via intermediate relations.
See Section \ref{sec:tuning-datalog-analysis} for hints on tuning the performance
of Datalog analyses.

Running a Datalog analysis is no different from running any other kind of analysis
in Chord.  See Chapter \ref{chap:running-analysis} for how to run an analysis.

\section{Tuning Performance}
\label{sec:tuning-datalog-analysis}

>>>>

\xname{datalog}
\chapter{Datalog Analysis}
\label{chap:datalog}

A common way to rapidly prototype an analysis in Chord is using a declarative
logic-programming language called Datalog.  This chapter describes all aspects
of Datalog analyses in Chord.  Section \ref{sec:writing-datalog} explains how to
write and run a Datalog analysis.  Section \ref{sec:tuning-datalog} explains how
to tune its performance.  Finally, Section \ref{sec:bdd} explains the
representation of BDDs (Binary Decision Diagrams) which are a data structure
central to executing Datalog analyses.

\section{Writing a Datalog Analysis}
\label{sec:writing-datalog}

A Datalog analysis declares a bunch of input/output program relations, each over
one or more program domains, and provides a bunch of rules (constraints)
specifying how to compute the output relations from the input relations.  It can
be defined in any file with suffix {\tt .dlog} in any directory in the path
specified by property \code{chord.dlog.analysis.path}.  An example Datalog
analysis is shown below:

@@

The ``\code{.include "<DOM_NAME>.dom"}'' lines specify each domain named
\code{<DOM_NAME>} that is needed by the Datalog analysis, i.e., each domain over which
any relation that is input/output by the Datalog analysis is defined. 
The declaration of each such relation specifies the relation's schema:
all the domains over which the relation is defined.
If the same domain appears multiple times in a relation's schema then
contiguous integers starting from 0 must be used to distinguish them; for instance,
in the above example, {\tt candidate} is a binary relation, both of whose
attributes have domain {\tt E}, and they are distinguished as {\tt E0} and {\tt E1}.

@@

Each Datalog analysis rule is a Horn clause of the form
``{\tt R(t) :- R1(t1), ..., Rn(tn)}"
meaning that if relations {\tt R1}, ..., {\tt Rn} contain tuples {\tt t1}, ..., {\tt tn}
respectively, then relation {\tt R} contains tuple {\tt t}.
A backslash may be used at the end of a line to break long rules for readability.
The Datalog analysis solver bddbddb used in Chord does not apply any
sophisticated optimizations to simplify the rules; besides the BDD variable order,
the manner in which these rules are expressed heavily affects the performance of
the solver.  For instance, an important manual optimization involves breaking down
long rules into multiple shorter rules communicating via intermediate relations.
See Section \ref{sec:tuning-datalog} for hints on tuning the performance
of Datalog analyses.

Running a Datalog analysis is no different from running any other kind of analysis
in Chord.  See Chapter \ref{chap:running} for how to run an analysis.

\section{Tuning Performance}
\label{sec:tuning-datalog}

### 2011-04-15 main/doc/program.tex
more documentation

\xname{program_representation}
\chapter{Program Representation}
\label{chap:program-representation}

Chord uses \xlink{Joeq}{http://joeq.sourceforge.net/} to translate
Java bytecode, one class file at a time, into a three-address-like
intermediate representation of the input Java program called {\it
quadcode}.  This chapter describes all aspects of quadcode and how it
relates to bytecode.  It first explains how to pretty-print bytecode
and quadcode (Section \ref{sec:pretty-printing}) which is useful for
debugging analyses and deciphering their output.  The remaining
sections describe the quadcode representation along with the API of
Joeq and Chord for navigating it.  Briefly, the representation
consists of a set of classes that may be loaded
(Section \ref{sec:program}).  Each class has a set of fields and
methods, collectively called members of the class
(Section \ref{sec:class-members}).  The representation of a concrete
method (Section \ref{sec:methods}) consists of a control-flow graph
(CFG).  The representation of a CFG (Section \ref{sec:cfgs}) consists
of a set of registers and a set of basic blocks.  Each basic
block contains zero or more primitive statements called quads
(Section \ref{sec:quads}).  Finally, the most common way to traverse
all quads is discussed (Section \ref{sec:traversing}).

@@

To pretty-print the bytecode representation of a class, run the following command:
\begin{framed}
\begin{verbatim}
javap -classpath <...> -private -verbose <CLASS NAME>
\end{verbatim}
\end{framed}

@@

\begin{itemize}
\item
{\tt <CLASS NAME>} is the fully-qualified name of the class whose
bytecode is to be printed (\code{test.HelloWorld} in our example).
\item
\code{<...>} is the classpath of that class (\code{examples/hello_world/} in our example).
\end{itemize}

@@

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<...> -Dchord.print.classes=<CLASS NAME> \
    -Dchord.verbose=0 -Dchord.out.file=<FILE NAME> run
\end{verbatim}
\end{framed}

@@

\begin{itemize}
\item
\code{<...>} is the path of a directory (\code{examples/hello_world/} in our example) that is expected to
contain a file named \code{chord.properties} which defines
properties \code{chord.main.class} and \code{chord.class.path}
specifying the main class and the classpath of the input Java program
(alternatively, these two properties can be defined directly on the
above command line).
\item
{\tt <CLASS NAME>} is the name of the class whose quadcode is to be
printed.
\item
{\tt <FILE NAME>} is the name of a file to which the quadcode is to be
dumped.
\end{itemize}

@@

This and the following sections describe the quadcode representation
along with the API of Joeq and Chord for navigating it.
This API is contained in
packages \javadoc{chord.program}{chord/program/package-tree.html}, \javadoc{joeq.Class}{joeq/Class/package-tree.html},
and \javadoc{joeq.Compiler.Quad}{joeq/Compiler/Quad/package-tree.html}.

@@

See Chapter \ref{chap:computing-scope} for how Chord determines which
classes may be loaded and which methods may be called.

@@

\begin{framed}
\begin{verbatim}
joeq.Class.jq_Type
  |
  |--- joeq.Class.jq_Primitive
  |
  |--- joeq.Class.jq_Reference
            |
            |--- joeq.Class.jq_Class
            |
            |--- joeq.Class.jq_Array
\end{verbatim}
\end{framed}

@@

\begin{framed}
\begin{verbatim}
FieldDescriptor : FieldType
      FieldType : BaseType | ObjectType | ArrayType
       BaseType : B | C | D | F | I | J | S | Z
     ObjectType : L <classname> ;
      ArrayType : [ ComponentType
  ComponentType : FieldType
\end{verbatim}
\end{framed}

The characters of \code{BaseType}, the {\tt L} and {\tt ;}
of \code{ObjectType}, and the {\tt [} of
\code{ArrayType} are all ASCII characters.
The {\tt <classname>} represents a fully qualified class or interface
name.  The interpretation of the field types is as shown in the below
table:

@@

\begin{framed}
\begin{verbatim}
   MethodDescriptor : ( ParameterDescriptor* ) ReturnDescriptor
ParameterDescriptor : FieldType
   ReturnDescriptor : FieldType | V
\end{verbatim}
\end{framed}

A parameter descriptor represents the type of an argument of a method.
A return descriptor represents the type of the return result of a
method.  The character \code{V} indicates that the method returns no
value (its return type is void).

@@

The control-flow graph (CFG) of each method consists of a set of registers,
called the register factory, and a graph whose nodes are basic blocks and
whose edges denote flow of control between basic blocks.

@@

\subsection{Register Factory}

@@

\subsection{Basic Blocks}

Each CFG has a set of basic blocks each of which contains a
straight-line sequence of zero or more primitive statements called quads
(Section \ref{sec:quads}).  Each CFG is guaranteed to contain at least
two basic blocks: a unique entry basic block with no incoming edges
and a unique exit block with no outgoing edges.  The entry and exit
basic blocks do not contain any quads.

@@

\begin{framed}
\begin{verbatim}
Operator
    |    Move, Phi, Unary, Binary, New, NewArray, MultiNewArray, 
    |--- Getstatic, Putstatic, Getfield, Putfield, ALoad, AStore,
    |    CheckCast, InstanceOf, ALength, Return
    |
    |--- Branch
    |       |--- IntIfCmp, Goto, Jsr, Ret, LookupSwitch, TableSwitch
    |
    |--- Invoke
    |       |--- InvokeVirtual, InvokeStatic, InvokeInterface
    |
    |--- Monitor
            |--- MONITORENTER, MONITOREXIT
\end{verbatim}
\end{framed}

>>>>

\xname{program}
\chapter{Java Program Representation}
\label{chap:program}

Chord uses \xlink{Joeq}{http://joeq.sourceforge.net/} to translate
Java bytecode, one class file at a time, into a three-address-like
intermediate representation of the input Java program called {\it
quadcode}.  This chapter describes all aspects of quadcode and how it
relates to bytecode.  It first explains how to pretty-print bytecode
and quadcode (Section \ref{sec:pretty-printing}) which is useful for
debugging analyses and deciphering their output.  The remaining
sections describe the quadcode representation along with the API of
Joeq and Chord for navigating it.  Briefly, the representation
consists of a set of classes that may be loaded
(Section \ref{sec:program}).  The representation of each class consists
of a set of members (Section \ref{sec:class-members}) which are the fields and methods
of the class.  The representation of a concrete
method (Section \ref{sec:methods}) consists of a control-flow graph
(CFG).  The representation of a CFG (Section \ref{sec:cfgs}) consists
of a set of registers and a set of basic blocks linked by directed edges
denoting flow of control between basic blocks.
Each basic block contains zero or more primitive statements called quads
(Section \ref{sec:quads}).  Finally, the most common way to traverse
all quads is discussed (Section \ref{sec:traversing}).

@@

To pretty-print the bytecode representation of a class, run the following command:
\begin{framed}
\begin{verbatim}
javap -classpath <CLASS_PATH> -bootclasspath <BOOT_CLASS_PATH> -private -verbose <CLASS_NAME>
\end{verbatim}
\end{framed}

@@

\begin{itemize}
\item
\verb+<CLASS_NAME>+ is the fully-qualified name of the class whose
bytecode is to be printed (\code{test.HelloWorld} in our example).
\item
\verb+<CLASS_PATH>+ is the classpath of that class (\code{examples/hello_world/} in our example).
\item
\verb+<BOOT_CLASS_PATH>+ is the boot classpath; it is optional and must be supplied if
\verb+<CLASS_NAME>+ is a class from the JDK standard library (e.g., \code{java.util.ArrayList}) that has
been modified and written to a user-defined location (e.g., it has been instrumented by Chord and
written to \code{chord_output/boot_classes/}).
\end{itemize}

@@

\begin{framed}
\begin{verbatim}
ant -Dchord.work.dir=<WORK_DIR> -Dchord.print.classes=<CLASS_NAME> \
    -Dchord.verbose=0 -Dchord.out.file=<OUT_FILE> run
\end{verbatim}
\end{framed}

@@

\begin{itemize}
\item
\code{<WORK_DIR>} is a directory (\code{examples/hello_world/} in our example) 
that contains a file named \code{chord.properties} which defines
properties \code{chord.main.class} and \code{chord.class.path}
specifying the main class and the classpath of the input Java program.
Alternatively, these two properties can be defined directly on the
above command-line.
\item
\code{<CLASS_NAME>} is the fully-qualified name of the class whose quadcode is to be printed
({\tt test.HelloWorld} in our example).  Each occurrence of a `{\tt \$}' in the class name
must be replaced by a `{\tt \#}'.
\item
\code{<OUT_FILE>} is the file to which the quadcode must be written; if left unspecified,
the quadcode is written to the standard output.
\end{itemize}

@@

This and the following sections describe the quadcode representation
along with the API of Joeq and Chord for navigating it.
This API is contained in
packages \javadoc{chord.program}{chord/program/package-summary.html}, \javadoc{joeq.Class}{joeq/Class/package-summary.html},
and \javadoc{joeq.Compiler.Quad}{joeq/Compiler/Quad/package-summary.html}.

@@

See Chapter \ref{chap:scope} for how Chord determines which
classes may be loaded and which methods may be called.

@@

\begin{verbatim}
                    jq_Type
                       |
      ------------------------------------
      |                                  |
jq_Primitive                       jq_Reference
                                         |
                          -------------------------------
                          |                             |
                      jq_Class                       jq_Array
\end{verbatim}

@@

\begin{verbatim}
FieldDescriptor : FieldType
      FieldType : BaseType | ObjectType | ArrayType
       BaseType : B | C | D | F | I | J | S | Z
     ObjectType : L <classname> ;
      ArrayType : [ ComponentType
  ComponentType : FieldType
\end{verbatim}

The characters of \code{BaseType}, the `{\tt L}' and `{\tt ;}'
of \code{ObjectType}, and the `{\tt [}' of
\code{ArrayType} are all ASCII characters.
The {\tt <classname>} represents a fully qualified class or interface
name.  The interpretation of the field types is as shown in the below
table:

@@

\begin{verbatim}
   MethodDescriptor : ( ParameterDescriptor* ) ReturnDescriptor
ParameterDescriptor : FieldType
   ReturnDescriptor : FieldType | V
\end{verbatim}

A parameter descriptor represents the type of an argument of a method.
A return descriptor represents the type of the return result of a
method.  The character `{\tt V}' indicates that the method returns no
value (its return type is void).

@@

The control-flow graph (CFG) of each method consists of a set of registers,
called the register factory, and a directed graph whose nodes are basic blocks and
whose edges denote flow of control between basic blocks.

@@

%\subsection{Register Factory}

@@

Besides the register factory, a CFG has a directed graph whose nodes are basic blocks and whose edges
denote flow of control between basic blocks.
Each basic block contains a straight-line sequence of zero or more primitive statements called quads
(Section \ref{sec:quads}).  Each CFG is guaranteed to contain at least
two basic blocks: a unique entry basic block with no incoming edges
and a unique exit block with no outgoing edges.  The entry and exit
basic blocks do not contain any quads.

@@

\begin{verbatim}
Operator
    |
    |--- Move
    |--- Phi
    |--- Unary
    |--- Binary
    |--- New
    |--- NewArray
    |--- MultiNewArray
    |--- Getstatic
    |--- Putstatic
    |--- ALoad
    |--- AStore
    |--- Getfield
    |--- Putfield
    |--- CheckCast
    |--- InstanceOf
    |--- ALength
    |--- Return
    |
    |--- Branch
    |       |
    |       |--- IntIfCmp
    |       |--- Goto
    |       |--- Jsr
    |       |--- Ret
    |       |--- LookupSwitch
    |       |--- TableSwitch
    |
    |--- Invoke
    |       |
    |       |--- InvokeVirtual
    |       |--- InvokeStatic
    |       |--- InvokeInterface
    |
    |--- Monitor
            |
            |--- MONITORENTER
            |--- MONITOREXIT
\end{verbatim}

### 2011-04-15 main/doc/properties.tex
more documentation

{\bf When:} Use this option to specify once and for all properties of the
Java program to be analyzed (e.g., property \code{chord.main.class} specifying the
name of that program's main class).
Chapter \ref{chap:program-setup} presents an example properties file 
that defines the program properties that are most commonly used.  Section \ref{sec:program-props}
presents all program properties that are recognized by Chord.

@@

This section describes properties that specify how the analysis scope of the input Java program is computed.
See Chapter \ref{chap:computing-scope} for more details.

@@

\code{chord.print.rels}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{[chord.out.dir]/<RELNAME>.txt} where
{\tt <RELNAME>} denotes the relation name. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This functionality must be used with caution as certain program relations, albeit represented compactly as BDDs, may contain
 a large number (e.g., millions) of tuples, resulting in voluminous output when printed in explicit form to a text file.  See Section
 \ref{sec:tuning-datalog-analysis} for a more efficient way to query the contents of program relations (namely, by using the {\tt debug}
 target provided in file {\tt build.xml} in Chord's main directory).
\end{quote}

@@

\code{chord.classic}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Whether to use the classic project (as opposed to the modern project).  See Chapter\ref{chap:analyses} for the difference
 between the two kinds of projects. \\
{\bf Default value:} \code{true}
\end{quote}

@@

%\item
%\code{chord.save.maps}
% bool
%Write to file \code{[chord.bddbddb.work.dir]/<...>.map} when saving program domain named {\tt <...>}.
%{\tt true}
%{\bf Note:} This functionality is useful for debugging Datalog programs using the {\tt debug} target provided in file {\tt build.xml} in Chord's main directory (see Section \ref{sec:tuning-datalog-analysis}).

>>>>

{\bf When:} Use this option to specify once and for all properties of the
Java program to be analyzed (e.g., property \code{chord.main.class} specifying the
name of that program's main class).
Chapter \ref{chap:setup} presents an example properties file 
that defines the program properties that are most commonly used.  Section \ref{sec:program-props}
presents all program properties that are recognized by Chord.

@@

This section describes properties that specify how the analysis scope of the input Java program is computed.
See Chapter \ref{chap:scope} for more details.

@@

\code{chord.print.rels}
\begin{quote}
{\bf Type:} string list  \\
{\bf Description:} List of names of program relations whose contents must be printed to files \code{[chord.out.dir]/<RELNAME>.txt} where
{\tt <RELNAME>} denotes the relation name. \\
{\bf Default value:} {\tt ""} \\
{\bf Note:} This functionality must be used with caution as certain program relations, albeit represented compactly as BDDs, may contain
 a large number (e.g., millions) of tuples, resulting in voluminous output when printed in explicit form to a text file.  See Section
 \ref{sec:tuning-datalog} for a more efficient way to query the contents of program relations (namely, by using the {\tt debug}
 target provided in file {\tt build.xml} in Chord's main directory).
\end{quote}

@@

\code{chord.classic}
\begin{quote}
{\bf Type:} bool \\
{\bf Description:} Whether to use the classic project (as opposed to the modern
project).  See Chapter\ref{chap:project} for the difference
 between the two kinds of projects. \\
{\bf Default value:} \code{true}
\end{quote}

@@

%\item
%\code{chord.save.maps}
% bool
%Write to file \code{[chord.bddbddb.work.dir]/<...>.map} when saving program domain named {\tt <...>}.
%{\tt true}
%{\bf Note:} This functionality is useful for debugging Datalog programs using
%the {\tt debug} target provided in file {\tt build.xml} in Chord's main
%directory (see Section \ref{sec:tuning-datalog}).

### 2011-04-15 main/doc/scope.tex
more documentation

\xname{computing_scope}
\chapter{Computing Analysis Scope}
\label{chap:computing-scope}

A pre-requisite to analyzing a Java program using any program analysis framework,
including Chord, is to compute the {\it analysis scope}: the set of methods
of the program to be analyzed.  Several scope construction algorithms (so-called
call-graph algorithms) exist in the literature that differ in scalability (i.e., how large
a program they can handle with the available resources) and precision (i.e., how small a
set of methods they deem is reachable).

Chord implements several standard scope construction algorithms.  Besides scalability and precision,
an additional metric of these algorithms in Chord that can be controlled by users is usability,
which concerns aspects such as excluding certain methods from being analyzed even if they
are reachable, and modeling Java features such as reflection,
dynamic class loading, and native methods.
These features affect which methods are
reachable but, in general, they cannot be modeled soundly by any program analysis framework.  The best
a framework can do is
 provide stubs for commonly-used native methods in the standard JDK library (e.g., the \code{arraycopy}
method of class \code{java.lang.System}), 
offer users a range of options on how to resolve reflection (e.g.,
an option might be running the program and observing how reflection is resolved), etc.

@@

The possible values of property \code{chord.scope.kind} are
[\code{dynamic}$|$\code{rta}$|$\code{cha}] (the default value is {\tt rta}).
The following subsections describe the scope construction algorithm
that Chord runs in each of these three cases.
In each case, Chord at
least expects properties \code{chord.main.class} and
\code{chord.class.path} to be set to the fully-qualified name of the
program's main class (e.g., \code{com.example.Main}) and the
program's application classpath, respectively.

\subsection{Dynamic Scope Construction}

\subsection{RTA Scope Construction}

@@

\subsection{CHA Scope Construction}

@@

@@

{\bf Note:} The value of each of the above properties is a list of {\it prefixes},
not {\it regular expressions}.  A valid value is \code{java.,com.sun.},
but not \code{java.*,com.sun.*}.

>>>>

\xname{scope}
\chapter{Analysis Scope Construction}
\label{chap:scope}

A pre-requisite to analyzing a Java program using any program analysis framework,
including Chord, is to compute the {\it analysis scope}: which parts of the
program to analyze.  Several scope construction algorithms (so-called
call-graph algorithms) exist in the literature that differ in scalability (i.e.,
how large a program they can handle with the available resources) and precision (i.e., 
how much of the program they deem is reachable).

Chord implements several standard scope construction algorithms.  Besides scalability and precision,
an additional metric of these algorithms in Chord that can be controlled by users is usability,
which concerns aspects such as excluding certain code from being analyzed even if it
is reachable, and modeling Java features such as reflection, dynamic class loading, and native methods.
These features affect which code are
reachable but, in general, they cannot be modeled soundly by any program analysis framework.  The best
a framework can do is
 provide stubs for commonly-used native methods in the standard JDK library (e.g., the \code{arraycopy}
method of class \code{java.lang.System}), 
offer users a range of options on how to resolve reflection (e.g.,
an option might be running the program and observing how reflection is resolved), etc.

@@

The possible values of property \code{chord.scope.kind} are
[\code{rta}$|$\code{cha}$|$\code{dynamic}] (the default value is {\tt rta}).
The following subsections describe the scope construction algorithm
that Chord runs in each of these three cases.
In each case, Chord at
least expects properties \code{chord.main.class} and
\code{chord.class.path} to be set to the fully-qualified name of the
program's main class (e.g., \code{com.example.Main}) and the
program's application classpath, respectively.

\subsection{Rapid Type Analysis}

@@

\subsection{Class Hierarchy Analysis}

@@

\subsection{Dynamic Analysis}

@@

{\bf Note:} The value of each of the above properties is a list of {\it prefixes},
not {\it regular expressions}.  A valid value is ``\code{java.,com.sun.}",
but not ``\code{java.*,com.sun.*}".
